% David Blain's professional resume
% Last Modified: Sun Dec 14 07:13:38 PM EST 2025
% Computer Science

% Elevator Pitch
% Employment History
% Projects
% Education

\documentclass[10pt, letterpaper]{report}
\usepackage[margin=0.3in]{geometry}
\usepackage{parcolumns}
\usepackage{enumitem}
\usepackage{nopageno}
\usepackage{parcolumns}
\usepackage{fontawesome5}
\usepackage{hyperref}

\IfFileExists{personal_info.tex}{
    \input{personal_info.tex}% chktex 27
}{
    \input{personal_info_stub.tex}% chktex 27
}

\setlength\parindent{0pt}

\newcommand{\sectionspacing}{2mm}
\newcommand{\postheaderspacing}{1mm}

% general command to align symbols better to the vertical axis of a single line
\newcommand{\vup}[1]{%
    \raisebox{\dimexpr(\fontcharht\font`X-\height+\depth)/2\relax}{#1}% chktex 41
}

% generic environment for the properly formatted sublists of each section
\newenvironment{marginmini}{%
    \begin{minipage}{\dimexpr\textwidth-1cm\relax}%
}{%
    \end{minipage}%
}

%generic itemize for closer formatting
\newenvironment{closeitems}{%
    \begin{itemize}[itemsep=0pt, topsep=0pt]%
}{%
    \end{itemize}
}

\begin{document}
    \begin{center}
        \LARGE{\textbf{David Blain}}

        \vspace{2mm}

        \small{\faMailBulk\hspace{1mm}}
        \large{\href{mailto:\myemail}{\myemail}}
        \large{\vup{\(\vert \)}}
        \small{\faPhone\hspace{1mm}}
        \large{\myphone}
        \large{\vup{\(\vert \)}}
        % These icons look better as "large". this is the default, but use it anyway to be explicit
        \large{\faGithub\hspace{1mm}}
        \href{https://github.com/drblain/resume}{drblain}
        \large{\vup{\(\vert \)}}
        \large{\faLinkedin\hspace{1mm}}
        \href{https://www.linkedin.com/in/davidrblain/}{davidrblain}

        \large{\myaddress}
    \end{center}
    \vspace{-1em}
    \textbf{Summary}
    \vspace{1mm}
    \hrule
    \vspace{\postheaderspacing}
    \hspace{12pt}
    \begin{minipage}{\dimexpr\textwidth-2cm}
        Software engineer with extensive experience designing, implementing, and testing systems across the full stack | from embedded firmware and systems engineering to user-space applications.
    \end{minipage}
    \vspace{\sectionspacing}

    \textbf{Employment}
    \vspace{1mm}
    \hrule
    \vspace{\postheaderspacing}
    \hspace{12pt}
    \begin{marginmini}
        \textbf{Leidos}, Tewksbury, MA

        \textit{Software Engineer II}, November 2024 | Present

        C\vup{++}, Linux (RHEL/CentOS), Qt, Boost, CMake, Azure, Google Test (GTest), Git, PostgreSQL

        \begin{closeitems}
            \item Refactored and redesigned integration of critical hardware monitoring systems in upgrade from Qt4 QScriptEngine to Qt5 QJSEngine, correcting Javascript syntax and providing developer ergonomics through metaprogramming.
            \item Architected test infrastructure for legacy and emerging code using Azure pipelines and GTest, enabling automatic CI/CD of build artifacts and providing 100\% test coverage for affected code.
            \item Participated in hands-on rapid prototyping and integration between the \textit{eXaminer} system and a new third-party system, enabling data fusion to reduce misclassification of threat objects while maintaining existing system performance.
            \item Led the design and implementation for conversion of existing Multi-View image data to a unified \textit{DICOS}-compliant standard, allowing the MV3D scanner to integrate with cutting edge aviation security screening management suites.
        \end{closeitems}

        \textbf{Raytheon Technologies}, Marlborough, MA

        \textit{Software Engineer I}, February 2022 | June 2024

        C\vup{++}, Java, MATLAB, Lua, GTest, Jenkins, Git/Clearcase, iTracker

        \begin{closeitems}
            \item Designed the software for a new method of calibration posing unique radar resource management and signal processing challenges in close collaboration with systems engineers, resulting in more accurate behavior analysis in testing.
            \item Corrected over 100 defects across software branches for multiple customers while interfacing with on-site integration and Dev-Ops teams, supporting critical demonstration and test deliverables while maintaining per-version requirements.
            \item Matured quickly into the role of `subject matter export' for one of the subsystems maintained by our scrum team, becoming the go-to contact across teams for questions about intent and changes to the area.
            \item Developed integration-level tests using MATLAB to provide total test coverage of simulated data through efficient computation and verification of expected behavior of the physical system relative to injected targets.
        \end{closeitems}
        
        \textbf{UConn Nanoelectronics Laboratory}, Storrs, CT

        \textit{Research Assistant}, May 2019 | March 2020

        MATLAB, Python, COMSOL Multiphysics, Stochastic Modeling, Technical Writing in IEEE Format

        \begin{closeitems}
            \item Engineered and validated high-fidelity simulations of nanoelectronic devices, extending existing mathematical models under varying boundary conditions.
            \item Conducted structural analyis on phase change materials exposed to Scanning Electron Microscopy (SEM), synthesizing experimental data into technical reports and presentations targeting a multi-disciplinary team audience.
            \item Mentored aspiring engineers in the Young Scholars Senior Summit (YSSS) program, delivering a curriculum on the fundamental principles of electric circuits and enabling the successful delivery of their final project demonstration.
        \end{closeitems}
    \end{marginmini}
    \vspace{\sectionspacing}

    \textbf{Personal Projects}
    \vspace{1mm}
    \hrule
    \vspace{\postheaderspacing}
    \hspace{12pt}
    \begin{marginmini}
        \textbf{\textit{`Rep It'} Exercise Logging and Analysis Mobile App}

        React Native (Expo), Typescript, SQLite, Tailwind CSS

        \begin{closeitems}
            \item Optimized mobile list rendering by implementing a reactive SQLite data pipeline with Drizzle ORM utilizing dynamic pagination on a normalized schema, improving initial load time and reducing memory footprint.
            \item Designed a responsive, theme-aware user interface using NativeWind (Tailwind CSS), ensuring a consistent user experience across iOS and Android devices.
        \end{closeitems}

        \textbf{\textit{`RS-Bright'} Automatic Brightness Adjustment Daemon}

        Rust, Bash, systemd, TOML, Debian packaging, OpenCV, X11

        \begin{closeitems}
            \item Producer-consumer thread model operating as a Linux systemd daemon to consume a system-level hotkey hook to execute the desired action in a lightweight way.
            \item Developed a physics-based luminance algorithm using OpenCV that applies gamma correction, weighted channel mixing, and feedback-loop mitigation to calculate ambient light levels.
        \end{closeitems}

    \end{marginmini}
    \vspace{\sectionspacing}

    \textbf{Education}
    \vspace{1mm}
    \hrule
    \vspace{\postheaderspacing}
    \hspace{12pt}
    \begin{marginmini}
        \textbf{University of Connecticut}, Storrs, CT

        \textit{Bachelor of Engineering, Major in Computer Science and Engineering, Minor in Mathematics}, August 2017 | May 2021

        Honors: Sophomore Honors, Magna Cum Laude

        Cumulative GPA:\@ 3.96/4.00
    \end{marginmini}
\end{document}